\textbf{Dynamic Hover Detection:\\Creating GUIs in Elm}

### 2014-01-01 paper/paper.tex
Clarified hoverables explanation

A typical use of \texttt{hoverables} is as follows. An initial
\texttt{a} is supplied that becomes the default value of
\texttt{events}. If \texttt{hoverable} is never applied, \texttt{events}
is constant. If it is, the \texttt{Element} argument of
\texttt{hoverable} in the record acts much like it does in
\texttt{hoverable} the top-level combinator: provides the static visual
appearance of the result \texttt{Element}, which also has hover
detection added. Hover events are boolean, so the function argument is
called on every such event to produce an \texttt{a} that becomes an
event on \texttt{events}.

What gives \texttt{hoverables} its plural name is that the record's
\texttt{hoverable} may be applied multiple times so that multiple
elements report their hover information on \texttt{events}. The
polymorphic \texttt{a} type exists to uniquely identify each element,
though it is also common for the \texttt{a} to also include the boolean
event. The simplest choice of \texttt{a} is simply \texttt{Bool}, and
this allows \texttt{hoverables} to implement \texttt{hoverable}:

@@

The \texttt{a -> Bool} function trivially becomes the identity. With a simple
change, we can create a function that acts on \texttt{Signal Element} instead of
\texttt{Element}:

@@

Notice that \texttt{pool.hoverable} is partially applied to \texttt{id}
purely, and then lifted on to the argument. This is possible,
ultimately, because \texttt{pool.hoverable} is pure.

>>>>

The first parameter to
\texttt{hoverables} denotes the initial value of the \texttt{events} signal
(signals in Elm must always be defined).
The \texttt{hoverable} part of the record takes an element and attaches hover
detection to it. Whenever the mouse hovers (or stops hovering) over the
element, an event is fired on the \texttt{events} signal. The value of that
event is determined by the \texttt{(Bool -> a)} parameter of the
\texttt{hoverable} function. In many cases, this will be \texttt{id} so that the
\texttt{events} signal is \texttt{True} when the element is being hovered upon
and \texttt{False} when it is not. However, the \texttt{(Bool -> a)} parameter
allows you to provide a different value on the \texttt{events} signal for different elements.

The more widely used \texttt{hoverable} function is implemented using
\texttt{hoverables}.

@@

There is a subtle, yet very important difference between \texttt{hoverables} and
\texttt{hoverable}. After providing the initial parameter to
\texttt{hoverables}, you are given a signal and a way to attach elements to that
signal. By applying the \texttt{hoverable} part of the record to multiple
elements, we can create a single signal which responds to the hover information
of those elements, instead of one signal per element. We can then exploit this
property to detect hoverable information on a signal of elements. As the value
of the input signal of elements changes, we attach the hover information to the
new element without having to create a new output signal.

@@

Notice that \texttt{pool.hoverable} is partially applied to \texttt{id}
purely, and then lifted on to the argument.
